Case Study: scRNA-seq (Mouse data, MAST method)

### 2018-04-06 datasets/scrnaseq/scrnaseq-human-mast.Rmd
Add more details to dataset description

This dataset (from PMC5810554) contains cells from four Glioblastoma patients, 
sampled from both the tumor core as well as the tissue peripheral to the tumor. 
We'll compare the Neoplastic cells in the tumor core vs periphery. We'll exclude 
the two samples where only a few neoplastic cells were found in the periphery.

>>>>

This dataset (from PMC5810554 [@darmanis2017]) contains cells from four Glioblastoma patients, 
sampled from both the tumor core as well as the tissue peripheral to the tumor. 
We'll compare the Neoplastic cells in the tumor core vs periphery. Here it is of 
interest to compare the gene expression profiles with cancerous cells that are part
of the primary tumor with those that have migrated, since these differences are
possibly related to metastasis. We'll exclude 
the two samples where only a few neoplastic cells were found in the periphery.

### 2018-04-06 datasets/scrnaseq/scrnaseq-mouse-mast.Rmd
Add more details to dataset description

*Add More detail on the experiments here*

We'll extract two conditions: No stimulation versus LPS at 150 min.

>>>>

This dataset (from PMC28396000 [@lane2017]) contains cells from a murine 
macrophage cell line that were studied for
the impact of stimulation of the innate immune transcription factor nuclear factor 
$\kappa$B (NF-$\kappa$B) on gene expression. Specifically, it is of interest to 
characterize the dynamics of global gene expression on activating immune response.
The NF-$\kappa$B was stimulated using 
a lipopolysaccharide (LPS)-dependent subunit fused to a fluorescent protein. 
Here we extract and compare two conditions and compare unstimulated cells versus
cells stimulated with LPS after 150 minutes.
